---
title: "TSF Task 1:Prediction using Supervised ML"
author: "Nirnoy Ghosh , Data Science & Business Analytics Intern, The Sparks foundation"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

## 1. Installtion and calling the required library
```{r ,message = FALSE}
#install.packages("readr")
#install.packages("dplyr")
library(readr)
library(dplyr)
```

## 2. Import the data and print the data.
```{r}
data=read.csv("C:/Users/ASUS/OneDrive/Desktop/Nirnoy/Placement/TSF/TSFtask1.csv",header=TRUE)
data
```

## 3. Checking the null value
```{r}
is.null(data)
```

### From the output it is clear that there is no null value

## 4. Checking some statistical property.
```{r}
summary(data)
```

## 5. Plot the data to understnd what kind of relationship has between two variables.
```{r}
#install.packages("ggplot2")
library(ggplot2)
ggplot(data = data, aes(x= Hours, y = Scores)) +
  geom_point() +
  geom_smooth(method= "lm",se = FALSE)
```

### The above diagram shows us the relationship of our model

## 6. Now we will calculate the coefficients of our model by using the given data.

```{r}
#Finding the coefficients of the data using linear model
data_coeff=lm(Scores~Hours, data= data)
data_coeff
```

### The model equation will be score= intercept + (hours * time) 
```{r}
summary(data_coeff)
```


### Here from the R squared valu we can say that 95.09% of scores can be explained by the study hours.  

## 7. We will calculate the expected or predicted score of the given data.

```{r}
coef(data_coeff)

data = data %>%
  mutate(predicted_value=fitted(data_coeff))
head(data)
barplot(as.matrix(data),col="light green")
```

## 8. Calculating the final score.
```{r}
score = coef(data_coeff)[[1]]+(coef(data_coeff)[[2]]*9.25)
score
```

### If a student studies for 9.25 hrs/ day,predicted score will be 92.91




---
Thank You
---